---
title: "ReproAssignment"
output:
  pdf_document: default
  html_document: default
---

## Reproducibility Assignment
[Github - jaydealexandra](https://github.com/jaydealexandra)  
Jayde MacMillan  
20068250  

### Project Info  
1/26/2022 

[Reproducibility Assignment](https://github.com/jaydealexandra/ReproAssignment.git)  
  
  
### Loads Data  
Loads the dplyr package into memory.
```{r}
library(dplyr)
```

Creates a dataframe called `fallo` using "FallopiaData.csv".
```{r}
fallo <- read.csv("~/BIOL 432/Projects/ReproAssignment/InputData/FallopiaData.csv")
```
  
### Manipulations and Calculations
  
Filters the dataframe `fallo` to include: biomass over 60, a new column titled 'TotalG' that contains the biomass in grams along with Taxon, Scenario, and Nutrients.
```{r}
fallo <- fallo %>%
  filter(Total>60) %>%
  transmute(TotalG = Total / 1000, Taxon, Scenario, Nutrients) 
```
  
Creates a custom function named `calcVector` that takes two parameters from the user and runs calculations based on the calculation type.
```{r}
calcVector <- function(dataToProcess, calcType){
  if (calcType == "Average"){
    print(mean(dataToProcess))
  } else if (calcType == "Sum"){
    print(sum(dataToProcess))
  } else if (calcType == "Observations"){
    print(length(dataToProcess))
  } else {
    print("Error: Invaild Calculation Type")
  }  
}
```

Uses `calcVector` to output the total number of observations in the Taxon column.
```{r}
calcVector(fallo$Taxon, "Observations")
```

Uses `calcVector` to output the average total grams for high and low nutrient conditions.
```{r}
calcVector(filter(fallo, Nutrients == "high")$TotalG, "Average")

calcVector(filter(fallo, Nutrients == "low")$TotalG, "Average")
```

Saves the formatted `fallo` data to "./Output/WrangledData.csv".
```{r}
write.csv(fallo, "./Output/WrangledData.csv")
```
  
  